%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Pre-Doctoral Fellow} % Job title
    {Cleveland Clinic Lerner Research Institute} % Organization
    {Cleveland, OH} % Location
    {Nov 2018-present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Retrovirally transduced a novel mouse model with alternatively-spliced Granculocyte Colony Stimulating Factor Receptor (CSF3R) to study its impact on neutrophil development.}
        \item {Cloned a novel CSF3R isoform (Class III) into lentiviral backbone and conducted the first CFU assay.} 
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Graduate Research Assistant} % Job title
    {Virginia Commonwealth University Department of Biomedical Engineering} % Organization
    {Richmond, VA} % Location
    {Sep 2013-May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Constructed silicone micro-pillars to determine the effects of mechanical stimuli on the growth of breast adipose stem cells and their role in mammary cancer development.}
        \item {Analyzed cell-derived traction forces and fibronectin growth in MATLAB to observe the relationship between cytoskeletal contraction and fibronectin assembly using microfabricated post-array detectors.}
        \item {Observed how bASC growth factor enriched  media influenced the growth of T4 cancer cells.} 
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Graduate Assistant} % Job title
    {VCU Graduate School of Enrollment Services} % Organization
    {Richmond, VA} % Location
    {Jan 2015-Jan 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted with documenting, scanning, linking, filing of student electronic records and email distribution of complete forms.}
        \item {Reported directly to the director of graduate school enrollment services with special projects on an as-needed basis.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Graduate Student Mentor} % Job title
    {VCU Graduate School Mentorship Program} % Organization
    {Richmond, VA} % Location
    {Sep 2014-May 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Actively participated in one-on-one weekly meetings with an undergraduate mentee over a one year period.}
        \item {Arranged opportunities to tour VCU Heatlh core facilities and meet with graduate program directors in order to promote interest in higher education.}
        \item {Organized workshops with a focus on writing personal statements, choosing graduate programs, and building portfolios.} 
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Taiwan Tech Trek Summer Intern} % Job title
{Taipei Medical University} % Organization
{Taipei, TW} % Location
{May 2012-Jul 2012} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Analyzed Taiwan's National Health Insurance Database to examine the association between viral warts and female breast carcinoma.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Undergraduate Research Assistant} % Job title
{University of Mary Washington} % Organization
{Fredericksburg,  VA} % Location
{May 2009-Apr 2011} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Studied developmental patterning of C. elegans and similar nematodes using differential interference contrast microscopy.}
    \item {Isolated, characterized, and identified new Caenorhabditis species for comparative developmental studies. 18S ribosomal subunits of new relevant sister species were sequenced and submitted to GenBank.}
    \item {Constructed phylogenic trees based on sequence similarities to study their morphological evolution.}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
